\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces

### 2014-08-13 doc/sui14/iteration1.tex
add physical description, will update more later

As for the qualitative feedback, 11 out of 14 participants preferred IR selection over list mode (two preferred list, one was undecided). While both interfaces were judged similarly on overall ease of connecting, IR selection was perceived to be more direct and \changes{pleasant}. One user noted benefit of {\em IR selection}  \studyquote{allowing users to focus on the targeted objects instead of the screen}. \achal{This seems rather weak... Don't really need all the quotes.} One subject called it \studyquote{natural to interact with things just by looking at them}. Another mentioned that \studyquote{it's really convenient that what I'm looking at is what I'm targeting}.

>>>>

\changes{Most participants walked one or two steps during each task. In the survey we asked \studyquote{When you have multiple candidate targets within sight, which method for selecting between did you use?} (multiple choice), among 16 participates, X\% chose {\em adjust head so that only one candidate is signaled}, Y\% chose {\em walk closer to the candidate for a better result}, and only Z\% chose {\em tap (to enter refinement stage) and then choose between list}. \sean{will update numbers and add a few sentences here.}}
As for the qualitative feedback, 11 out of 14 participants preferred IR selection over list mode (two preferred list, one was undecided). While both interfaces were judged similarly on overall ease of connecting, IR selection was perceived to be more direct and \changes{pleasant}. One user noted benefit of {\em IR selection}  \studyquote{allowing users to focus on the targeted objects instead of the screen}. \achal{This seems rather weak... Don't really need all the quotes.} One subject called it \studyquote{natural to interact with things just by looking at them}. Another mentioned that \studyquote{it's really convenient that what I'm looking at is what I'm targeting}.
